\section{Related Work}

There are a few ways of approaching the problem of determining a person's blood alcohol content. One approach is to model mathematically the elimination of ethanol in the human body. In this case, the Widmark equation, published in 1932 by E.M.P. Widmark, is a very popular one, \begin{equation}
•C=\frac{A}{rW}-(\beta t)
\end{equation} where C is the BAC, r and $\beta$ are empirically determined constants, A is the mass of the consumed alcohol, and W is the body weight of the person.
	These days, there have been several improvements and variants. Douglas Posey and Ashraf Mozayani published an excellent article comparing this model using parameters determined by different researchers and discussing different models \cite{Posey:2007}. They found that the Widmark equation tends to overestimate, and that there can be significant discrepancy between the results of the different models. Despite that, they do provide a rough estimate. The problem is that these models also require a good deal of information that prohibit their use in a non-intrusive, drunkenness warning system.

Another approach to the problem is simply to directly measure the BAC, such as with the recent investigations into the use of transdermal ethanol sensors. Transdermal sensing provides a more discreet way to measure BAC, but this method is accompanied by the problem of a significant time lag between the sensed alcohol concentration and actual blood alcohol concentration. Gregory Webster and Hampton Gabler closely investigated this problem. They found that the lag is predictable, but variable, and requires additional information about the drinks taken to accurately predict \cite{Webster:2007}.

In 2014, James Baldwin applied for a patent on a wearable blood alcohol measuring device \cite{Baldwin:2014} as a non-invasive, discreet, and wearable method of continuously predicting blood alcohol content. Baldwin's method involves the use of a transdermal ethanol sensor and a method of predicting future BAC given the user's intended consumption. It is also meant to provide guidance for the user as to when to stop in order to be at a certain BAC by a previously specified time. Baldwin's invention is very similar to this project with the only major difference being that it uses a wearable transdermal ethanol sensor to directly measure BAC instead of using common sensors found in smartwatches and a prediction model, such as we do, in order to predict BAC. The use of a transdermal ethanol sensor is proven to have many issues, mostly in the delay between consumption and sensing \cite{Webster:2007}. Another issue is that it requires a special sensor that would only be used for this purpose. Our project improves on this issue by using a common device that many already own for various other reasons. Also, due to our approach for monitoring drunkenness, our method may provide more immediate predictions.  

In 2015, Koukiou and Anastassopoulos published a paper on using a neural network to identify drunkenness from thermal infrared imagery \cite{Koukiou:2015}. Different neural networks were trained on different parts of the face in order to determine which areas can be used to discriminated "a drunk from a sober person." Their findings showed that the forehead was the main feature to change thermal behavior from the consumption of alcohol. Later, the whole face was used to train a neural structure which showed high performance on discrimination. The results showed that the forehead and the nose are the areas of the face that were most prominent in drunk people. A neural networks was then trained on the forehead of only one person which was then used on other persons in order to determine those who were drunk. The results had a success rate of around 90\%. This study shows that there is a correlation between skin temperature and drunkenness, which is applicable to our research because of the skin temperature sensor found on many smartwatches. This project has many similar applications as our would, such as being able to be incorporated into ignition interlock systems or to give evidence to authorities about intoxication in investigations. However, this system may not be able to be used by people to determine their own drunkenness as it requires a thermal infrared camera to be focused on the users face in order to do so. This would be difficult to do discreetly or conveniently. 

There is also research going into using various sensors for health applications, many using a machine learning approach to do so. 

In "Multi-Sensor Fusion for Enhanced Contextual Awareness of Everyday Activites with Ubiquitous Devices" \cite{Guiry:2014}, the authors attempt to use the sensors in smartphones and smartwatches to identify various daily activities such as walking, running, cycling, sitting, etc. It also identified whether or not the user is indoors or outdoors. Collected data was then used to train 5 different machine learning algorithms: C4.5, CART, Na\"{\i}ve Bayes, Multi-Layer Perceptrons, and Support Vector Machines. Results showed promise, with one model for inside/outside classification being 100\% correct. This study shows that the use of multiple sensors improves classification accuracy. For our research, we may be able to improve BAC prediction by recognizing when the user is taking a drink. This research shows that machine learning models can be used to label collected sensor data to certain activities.

Study has been done in using accelerometers to detect seizures \cite{Milosevic:2014} and using smartphones and smartwatches to monitor Parkinson Disease \cite{Sharma:2014}. In research on the detection of seizures \cite{Milosevic:2014}, researches use accelerometers on each wrist and ankle and a machine learning model in order to detect epileptic convulsions. Results included detection of 19 out of 23 seizures that were longer than 30 seconds each, with only a false alarm rate of .39 per hour. SPARK, a proposed framework that uses smartphones and smartwatches to monitor for symptoms of Parkinson Disease \cite{Sharma:2014}, including speech analysis, facial tremors, dyskinesia, freezing of gait. SPARK is for users to have their body motions monitored for dyskinesia and freezing gait while also having the user read paragraphs for speech analysis or pointing the camera for facial analysis. SPARK will also provide recommendations to physicians based on the collected information, such as changes in medication. SPARK is still being tested in order to determine the usefulness of such a framework for those who would use it. It is noted that there are limitations to it in that many patients will not be able to adopt the technologies required for it. There are also many issues, such as sensor misplacement and log errors, that can be encountered. Both these project show a desire to create health-based monitoring applications. 

%Current list of applications on smart watch, and their novelty. Current Prediction of BAC and associated ML algorithms